---
title: "Target Markdown"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(targets)
# Specify the project thanks to 
Sys.setenv(TAR_PROJECT = "gapminder")
```

Target Markdown is a powerful R Markdown interface for reproducible analysis pipelines, and the chapter at https://books.ropensci.org/targets/markdown.html walks through it in detail. This R Markdown report the example from the chapter. Try it out in both interactive and non-interactive modes, either by running the code chunks in different ways or setting the `tar_interactive` chunk option.

# Gapminder

## Globals

We first define some global options/functions common to all targets. The function below plots a histogram of ozone concentrations, and our histogram target will need it.

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
tar_option_set(packages = c("dplyr", "ggplot2", "readr", "tidyr", "purrr"))

gap_lm <- function(.data) {
  mutate(.data, year1950 = year - 1952) %>%
    ungroup() %>%
    nest(data = -c(country, continent)) %>%
    mutate(model = map(data, ~ lm(lifeExp ~ year1950, data = .x)))
}

extract_r2 <- function(.data) {
  mutate(.data,
         glance = map(model, glance),
         rsquare = map_dbl(glance, pluck, "r.squared"))
}
```

## Targets

Combine more than one with `list()`


A lot of format are available.

- `tarchetypes::tar_file()` will hash the file and keep track of its checksum
- `tar_fst_tbl()` uses [**fst**](http://www.fstpackage.org/fst/)

```{targets gapminder}
library(tarchetypes)

# Un comment 3 lines for future usage
#library(future)
#library(future.callr)
#plan(callr)


list(
  tar_file(gap_file, "gapminder.tsv"),
  # fst is Fast Serialization Table
  tar_fst_tbl(gap, read_tsv(gap_file), packages = "readr"),
  tar_group_by(gap_by, gap, continent, country),
  tar_target(model, gap_lm(gap_by), 
             pattern = map(gap_by),
             iteration = "group"),
  tar_target(r2, extract_r2(model), 
             pattern = map(model),
             packages = c("dplyr", "broom", "purrr")),
  tar_target(r2_coeff, mutate(r2, tidy = map(model, tidy)),
             packages = c("dplyr", "broom", "purrr"))
)
```

The report is also a `target`, so rendering is triggered by any upstream dependencies found thanks to `tar_read()` calls

```{targets render_report}
tar_render(report, "report_gap.Rmd")
```

## Pipeline

### Direct Acyclic Graph

The `targets` dependency graph helps your readers understand the steps of your pipeline at a high level.

```{r}
tar_visnetwork()
```

### Run what needs to be

```{r}
tar_make(reporter = "verbose_positives")

#future make:
#tar_make_future(workers = 2)
```

`reporter = "verbose"` will print 142 lines like:

```
[...]
#> ✓ skip branch r2_e37e778f
#> ✓ skip branch r2_2a83156a
#> ✓ skip branch r2_20bd35cf
#> ✓ skip branch r2_44a67b3b
#> ✓ skip branch r2_196e8670
#> ✓ skip branch r2_367a1d6e
#> ✓ skip branch r2_c7514b5d
[...]
```

- Re-check the DAG

```{r}
tar_visnetwork()
```




```{r, eval = FALSE}
tar_make_future(workers = 2)
```

